---
title: "Creating Share Price Graphs with R"
author: "Alexander Klar"
date: "December 27, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## Intro

In this short presentation I will

- load share price data from Yahoo using the quantmod package
- convert the data into a data frame
- create a graph using the plotly package

## The code (1/2)

```{r stocks1, cache = TRUE, echo = TRUE, results="hide"}
#load packages
suppressMessages(library(quantmod))
suppressMessages(library (plotly))

# not setting a seed gives a warning message in plotly
set.seed(2016-12-27)
# load share price data for selected companies
# no time filter => data starting 2007
suppressMessages(getSymbols(c('ORCL', 'IBM', 'MSFT', 'GOOGL', 'AMZN')))
```


## The code (2/2)
```{r stocks2, cache = TRUE, echo = TRUE, results="hide"}
# convert date and close price into a data frame for each stock 
oracle <- data.frame(date = index(ORCL$ORCL.Close), 
            close = as.numeric(ORCL$ORCL.Close), stockname = "Oracle")
amazon <- data.frame(date = index(AMZN$AMZN.Close), 
            close = as.numeric(AMZN$AMZN.Close), stockname = "Amazon")
google <- data.frame(date = index(GOOGL$GOOGL.Close), 
            close = as.numeric(GOOGL$GOOGL.Close), stockname = "Google")
ibm <- data.frame(date = index(IBM$IBM.Close), 
            close = as.numeric(IBM$IBM.Close), stockname = "IBM")
microsoft <- data.frame(date = index(MSFT$MSFT.Close), 
            close = as.numeric(MSFT$MSFT.Close), stockname = "Microsoft")
# data frame used for the plot
stocks <- rbind(oracle, amazon, google, ibm, microsoft)

# create object to plot 
stockplot <- plot_ly(stocks, x = stocks$date, y = stocks$close, 
            color = stocks$stockname, type = "scatter",  mode = "lines")
```

## The Result

Closing Price by Date:
```{r plotstocks, dependson=stockplot, echo = FALSE}
stockplot
```

## Summary

You have seen, how easy it is to 

- get external financial data using quantmod
- visualize data using plotly (although quantmod has cool visualisations as well)